Teaching a Class to Grade Itself using Game Theory

### 2013-09-08 Primes Write up.tex
Got rid of you/your

So assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
	If you don't grade the paper, you don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
	If you do grade, you use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1

If the grader's partner gives the paper its true grade:
	If the grader doesn't grade the assignment, you will give it a 100 and so the grader's contribution score is -1. So their happiness is H(your original grade) - 4.
	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).

>>>>

So assuming that the student's partner gives the paper a 100, which is the best thing they could do if they don't grade, then
	If they don't grade the paper, they don't use any effort. So the student's happiness will H(the student's grade on the original assignment). Contribution score = 0
	If they do grade, they use 1 unit of effort by default. But, the student's happiness will be H(the student's grade on the original assignment) + 3. Contribution score = 1

If the grader's partner gives the paper its true grade:
	If the grader doesn't grade the assignment, they will give it a 100 and so the grader's contribution score is -1. So their happiness is H(their original grade) - 4.
	If the grader does grade the assignment, they and their partner gave the same grades, so they get a contribution score of 0. This means that their happiness is H(their original grade).
